Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification

### 2021-09-13 article.tex
formatting

\newcommand{\nospell}[1]{#1}
\setlength\headheight{24pt}
\newcommand\figcaption[1]{\Description{#1}\caption{#1}}
\raggedbottom

@@

Fig.~\ref{fig:example} defines constructor arguments only for
the \ff{Fraction} class. The class \ff{User} don't have any arguments. The class
\ff{SuD} is a pre-defined class without arguments. The class \ff{Float} is a
pre-defined class with one argument.

@@

Third, developing a requirements specification with the language requires RE
engineers to understand key principles of ``object thinking''~\citep{west04},
like ``everything is an object'' and ``objects expose behavior, not state.''
Initial training was required in two projects.

>>>>

\newcommand{\nospell}[1]{#1}
\setlength\headheight{24pt}
\newcommand\figcaption[1]{\Description{#1}\caption{#1}}
\raggedbottom
\tolerance=2000

@@

Fig.~\ref{fig:example} defines the arguments of the constructor only for
the \ff{Fraction} class. The class \ff{User} don't have any arguments. The class
\ff{SuD} is a pre-defined class without arguments. The class \ff{Float} is a
pre-defined class with one argument.

@@

Third, developing requirements specification with the language requires RE
engineers to understand key principles of ``object thinking''~\citep{west04},
like ``everything is an object'' and ``objects expose behavior, not state.''
Initial training was required in two projects.
